\documentclass[twoside,single]{lion-msc}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{adjustbox}
\usepackage{tablefootnote}


\title{Clustering and Physical Properties of CO Emitters in Wide ASPECS}
\author{Jacob Bieker}
\degree{Master of Science}   
\major{Astronomy}
\studentid{2153246}
\supervisor{Dr. Jacqueline Hodge}
\correctorone{Dr. Rychard Bouwens (designated by J. Hodge)}
\correctortwo{Prof. Paul van der Werf} 

\affiliation{Leiden Observatory, Leiden University} 
\address{P.O. Box 9513, 2300 RA Leiden, The Netherlands} 

\abstract{In this research, data from Wide ASPECS is used to look at the clustering and properties of blindly selected CO emitters within the GOODS-South region of the sky. The frequency range covered enables the identification of CO emission lines up to a $z = 4.4$. The survey builds on the results of the ASPECS Pilot and Large Program surveys, with 35 potential CO line candidates found, and 3 lines matched with counterparts. The properties of these counterparts are examined to determine the physical properties of CO emitters within the field. There is clear increase in the two-point correlation function at higher fidelities for the CO line candidates, suggesting that there are real sources present, although the results are quite noisy. A comparison of the scale radius, $r_0$, inferred for these CO sources to the $r_0$ obtained for other populations of galaxies is performed. These results build toward calculating the first direct constraints on the clustering bias of CO emitters, and therefore their halo mass.}

\begin{document}

\maketitle

\pagenumbering{roman}
\setcounter{page}{2}
\tableofcontents
\cleardoublepage

\pagenumbering{arabic}
\setcounter{page}{1}
\chapter{Introduction}
%In general, I think the introduction is a bit messy, this is my suggestion:

%I would start the introduction with what you wrote in 1.1 section (but I wouldn't use the title "creating galaxies", just write after the introduction title).

%Then I would add a section called soemthing like "Molecular gas in galaxies", and put there the first 4 lines of your current introduction (Gas is the building...volumes of space) and then continue with what you wrote in your current 1.2 section (but I would to avoid the first paragraph where you say that stars are easy to detect).

%After that I would create a subsection called something like "Blind surveys of molecular gas" and put what you wrote in your section 2.1 (but not using the previous work title).

%Finally I would add a sebsection called "This thesis" and I would put the second parragraph of your current intriduction (This project is focused on using ....CO emitters) as editted according to my comment (see below).

%Then put the 2 last parragraph you wrote in section 1.4 (This report is organized...ASPECS).

The initial seeds that created the large scale structure of the universe all came from tiny perturbations which are observable today in the cosmic microwave background. These slight differences in density caused dark matter to clump together. These clumps of dark matter pulled in gas, creating giant clouds. Some of the gas further collapsed to create stars, which in turn formed galaxies.

As a result of this process, galaxies are composed of gas, dust, dark matter, and stars in various quantities, and so evolve in different ways. Starburst galaxies, for example, are undergoing intense episodes of star formation, and therefore are very bright and use up the gas available to them fairly quickly, in $<$ 0.1 Gyr. On the other hand, main sequence galaxies tend to have much lower star formation rates, and therefore deplete their gas at a much slower rate, around 1 Gyr \cite{scoville2017evolution, silverman2015higher}.

These differences in behavior result a diverse phenomenology of galaxies. Young stars, for example, tend to emit most of their light in the ultraviolet, and so galaxies with large amounts of ultraviolet light tend to have had large amounts of recent star formation. Dust, on the other hand, tends to absorb the ultraviolet and visible light emitted by stars and re-emits the light at longer wavelengths, such as the infrared. By looking at all the light that a galaxy emits therefore, the properties and makeup of a galaxy can be estimated.

\section{Molecular Gas in Galaxies}

Gas is the building block of stars and galaxies, and molecular gas in the interstellar medium (ISM) is the fuel for star formation \cite{decarli2019alma}. This gas can inform us about the evolution of galaxies and large scale structure in the universe, especially as observations cover larger and larger volumes of space. %Using radio and submm telescopes, such as the Atacama Large Millimeter/submillimeter Array (ALMA), this gas can be observed through looking for the transition lines of carbon monoxide (CO). 

%Parts of a galaxy are easy to observe, and other parts are not. Stars are relatively simple to observe; simply point a telescope like Hubble for long enough at a particular point in the sky and stars become visible. Gas on the other hand, especially the cold gas that collapses to form stars, is much more difficult to detect. % Wouldn't put this here, so delete?

Most of the gas in the universe is made up of hydrogen. Unfortunately for astronomers, molecular hydrogen, $H_2$, is only bright enough to observe when it is relatively hot, around 500 Kelvin \cite{decarli2019alma}. As the cold gas that births stars does not usually reach 500 Kelvin, carbon monoxide (CO) is observed instead. CO is the second most common molecule after $H_2$, but has the advantages of having bright rotational transitions that can be observed all the way to very high redshifts \cite{carilli2013cool}. The energy leveels of CO are easily populated even at low temperatures (a few Kelvin), and so the lines arise also in the cold, star forming medium \cite{carilli2013cool}. Additionally, CO emission is thought to be a good tracer of molecular hydrogen, and the the amount of $H_2$ gas present can be inferred from the amount of CO that can be detected by using a conversion factor $\alpha_{CO}$ \cite{bolatto2013co}. 

The CO molecular gas can be observed through the detection of the CO emission lines which show up in the radio and (sub)mm spectrum, requiring telescopes such as ALMA and the Jansky Very Large Array (VLA) to be used to detect them on Earth \cite{decarli2019alma}. 

\section{Blind Surveys of Molecular Gas}

There have been two main types of surveys for searching for CO emitters in the universe, targeted and blind surveys. In targeted surveys, targets are chosen based on some type of preselection, such as star formation rate, mass, or some other parameter \cite{tacconi2018phibss}, and are looked at specifically to see what CO emission can be found in that galaxy or galaxies. While these surveys have given useful information on the role gas plays in these galaxies, the preselection process means that there could be a bias in our knowledge of CO. For example, these surveys could miss out on dark, gas-rich galaxies that are hard to detect, giving us an incomplete picture of the variety of galaxies with gas and CO emission in the universe. 

Blind surveys are the opposite of targeted surveys. Instead of choosing the targets and looking at them specifically, blind surveys choose an area of the sky and search for any CO emission within that cosmic volume, allowing for any emission above the sensitivity limit of the survey to be found. This allows for a sort of census of all the gas within a cosmic volume \cite{decarli2019alma}. 

Previous blind surveys include the COLDz survey in the GOODS-North region, the PdBI survey, as well as the first two surveys in the ASPECS program, ASPECS Pilot and ASPECS Large Program.

The PdBI survey was a molecular line survey in the Hubble Deep Field North (HDF-N) in 3mm using the IRAM Plateau de Bure Interferometer (PdBI) \cite{decarli2014molecular}. This survey was designed to cover all CO transitions detectable above z $>$ 2, and well as covering the redshift ranges of z $<$ 0.45, and 1 $<$ z $<$ 1.9. The survey identified 17 line candidates, with most of the candidates falling in intermediate redshifts (z $<$ 3), and with 7 of the line candidates matching to galaxies in their catalog \cite{decarli2014molecular}.

COLDz, or the CO Luminosity Density at High-z (COLDz) targeted CO(1-0) emission from galaxies at redshifts between 1.95-2.85 and CO(2-1) emission between z = 4.91 - 6.70 using the Very Large Array (VLA)\cite{pavesi2018co}. This survey covers a wide area of around 51 arcminute$^2$, as well as a roughly 9 arcminute$^2$ area much more deeply. This survey blindly selected starburst and massive main sequence galaxies in the GOODS-North and COSMOS fields. COLDz found seven secure CO line detections, and 57 above their S/N threshold, including many that did not have optical or near infrared counterparts, suggesting that those candidates could potentially be from a population of gas-rich, but optically dark galaxies \cite{pavesi2018co}.

The ASPECS Pilot and Large Programs both looked at regions in the Hubble Ultra Deep Field. The Pilot program looked deeply in the 1.2mm and 3mm bands at a small, one arcminute region of the Hubble eXtremely Deep Field (XDF), obtaining a sensitivity of 0.1-0.25 mJy beam$^{-1}$ for the 3mm band, and 0.4-0.8 mJy beam$^{-1}$ for the 1.2mm band. The spectral coverage of the Pilot meant that it could detect CO transitions almost continuously from z = 0 to z = 8, as well as [CII] emission from z = 6 to z = 8 \cite{walter2016alma}. This allowed for the characterization of CO emitters all the way to a z = 8, as well as giving constraints on the knee of the CO luminosity function \cite{walter2016alma}. 

% Add how deeply it looked, how sensetive, in decarli paper
The Large Program looked wider, covering a roughly five square arcminute area of the Hubble Ultra Deep Field (HUDF) surrounding the ASPECS Pilot region. It was a 150 hour molecular deep field taken at 1.2mm and 3mm at a typical sensitivity of 0.2 mJy beam$^{-1}$ for the 3mm data, with analysis of the 1.2mm data currently ongoing \cite{decarli2019alma}. The greater volume probed by the Large Program allowed for constraining the density of gas in the universe, as well as better constraints on the CO luminosity function. The survey blindly revealed the molecular gas content in normal, star-forming main-sequence galaxies \cite{decarli2019alma}. 

%\section{From Observations to Models}

% Not here, but in Section 2.2.2
%All observations of a galaxy recorded in gamma and X-rays, visible light, infrared, radio and UV gives us part of the total spectral energy distribution (SED) of that galaxy. The more wavelengths a galaxy is measured in, the better constrained the SED, and the more complete our understanding of its energy distribution. Software, such as MAGPHYS \cite{da2008simple, da2015alma}, can use these observations to estimate a galaxy's physical parameters. These programs match the observed SED to precomputed models and output likelihood estimates for the properties of a given galaxy, such as the star formation rate, mass, dust temperature, and more.

%\section{Galaxies in Groups}

%Galaxies are not distributed randomly in the universe. On the largest scales, the universe is isotropic and homogeneous, but on smaller scales, galaxies tend to cluster in space. One way to quantify how densely packed a population of galaxies is to compute the so-called two-point correlation function. This allows for the measuring of the mass of the dark matter halos in which these galaxies reside \cite{hickox2011clustering}. For a certain redshift, the more clustered a population of galaxies is, the more massive the halo that they are in.

\section{This Thesis}

This project is focused on using the Wide ALMA Spectroscopic Survey in the Hubble Ultra Deep Field (Wide ASPECS), where ALMA has been used to observe one of the largest volumes of space yet for CO emission, on the order of 550,000 cMpc. This enables the ability to look at these CO emitters in bulk. Building upon the success of the previous ASPECS Pilot and Large Program surveys \cite{walter2016alma, decarli2019alma}, this research also works to cross-match detected CO lines with galaxies present in the survey volume, and builds the basis for future work with this data on constraining the bright end of the CO luminosity function, the contribution of luminous CO emitters to the cosmic density of molecular gas in galaxies, $\rho(H_2)$, and the clustering bias of CO emitters.

This report is organized as follows. Chapter 2 focuses on the setup of the survey, the methods used to detect and cross-match lines, and the properties of those matched galaxies. Chapter 3 focuses on the clustering of CO emitters in the survey volume, and compares the clustering of sources in this survey to those of other populations of galaxies. The final chapter, Chapter 4, contains the conclusions and possible future work. 

In this report, the $\Lambda$CDM cosmology is assumed, with $H_0$=70 km/s/Mpc, $\Omega_m$ = 0.3, and $\Omega_{\lambda}$ = 0.7, consistent with the results from the Planck Collaboration \cite{ade2016planck}. The analysis code used in this report is available \href{https://github.com/jacobbieker/Wide\_ASPECS}{here: https://github.com/jacobbieker/Wide\_ASPECS}. 

\input{survey.tex}

\input{clustering.tex}

\chapter{Conclusion}

In this research, data from Wide ASPECS was used to find CO line candidates, determine their properties, and find their clustering bias.

A catalog of 35 line candidates was created. This catalog was cross-matched to a catalog of previous detected galaxies in the same area. A total of three counterparts were found, and their properties were compared to the population of galaxies in the catalog. Two of those counterparts are on, or slightly above, the main sequence, while one has a much smaller stellar mass and star formation rate than would be expected for this survey. The other 32 potential sources could be optically dark, gas-rich galaxies that have evaded detection until now. 

Additionally, using the 35 CO lines in the catalog, the scale radius $r_0$ was computed for 1.5$<$z$<$3.5, and compared to other populations of galaxies. The scale radius seems to be similar to the $r_0$ of submillimeter galaxies \cite{10.1111/j.1365-2966.2011.20303.x}, and quasars in the Bo\"otes field \cite{hickox2011clustering}, while being larger than for Lyman break galaxies \cite{adelberger2005spatial}. While the extremely high noise in the measurement limits the constraints on the dark matter halos surrounding these CO emitters, a very loose estimate on the halo masses places them between $10^{12} h^{-1}M_{\odot}$ and $10^{13} h^{-1}M_{\odot}$.

% People will ask you if you tried to repeat your experiment by adopting priors in your line candidate selection. E.g., if you require that lines have an IRAC counterpart or a MUSE counterpart, you significantly drop the number of independent elements (and thus, the noise), which results in a superior fidelity. However, the drawback is that you introduce a selection function that you will have to account for in your clustering analysis. I suggest to add a few lines on this.

\section{Future Work}

While these results are interesting, they are quite tentative. The clustering results could be improved through performing the cross-correlation between the CO line candidates and the galaxy catalog \cite{hickox2011clustering, 10.1111/j.1365-2966.2011.20303.x, 10.1111/j.1365-2966.2008.14071.x}. 

Additional work could be done to verify the CO lines matched to galaxies, and investigate the reasons as to why the matched galaxies are much less massive and star forming than expected.

Priors could also be adopted for the line candidate search. For example, requiring lines have an IRAC or MUSE counterpart would reduce the number of independent elements, and therefore the noise, resulting in a higher fidelity. A drawback is that then the search is not a blind search, and the selection function would have to be accounted for in the clustering analysis.

Building off these results, more work could add constraints to the bright end of the CO luminosity function, as well as the contribution of luminous CO emitters to the cosmic density of molecular gas in galaxies, $\rho(H_2)$.

\appendix
\input{appendix.tex}

\bibliographystyle{unsrt}
\bibliography{refs}

\end{document}
